Floquet-Drude Conductivity in Dressed Quantum Hall Systems

### 2021-08-20 paper/v2.0/sections/5_floquet_drude_conductivity.tex
Spelling check

A general theory for the conductivity of a dressed system with the disorder was reported by Wackerl \textit{et al.} \cite{wackerl20,wackerlthesis20}. This theory, the general $x$-directional longitudinal DC-limit conductivity has been characterized as
\begin{equation} \label{eq:22}
  \begin{aligned}
    \sigma^{xx} = &
    \frac{-1}{4\pi\hbar A}
    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2}
    \left(
    -\pdv*{f}{\varepsilon }\right) \\
    &  \quad\times
    \tr
    \left\{
    {j}^x_0
    \left[
    \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
    \right]
    {j}^x_0
    \left[
    \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
    \right]
    \right\} d\varepsilon,
  \end{aligned}
\end{equation}
where $j^x_0$ is the $x$-directional electric current operator matrix elements' $0$-th Fourier component. Here, $\vb{G}^{r}(\varepsilon)$ and $\vb{G}^{a} (\varepsilon)$ are the retarted and advanced white noise disorder averaged Floquet Green function matrices \cite{wackerl20,wackerlthesis20}, respectively. These matrices are defined against the Floquet modes of the considering system. Here we have assumed that only $0$-th Fourier component of the current operator is contributing to the conductivity. In addition, $A$ is the area of the considered two-dimensional system, $f$ is the partial distribution function, and $\Pi$ is a function that can be chosen such that
\begin{equation} \label{eq:23}
    \Pi- \flatfrac{\hbar \omega}{2}
    \leq \varepsilon_N
    <
    \Pi + \flatfrac{\hbar \omega}{2}.
\end{equation}
Here $ \varepsilon_N$ are quasienergies of all relevant Floquet states, and $tr\{\cdot\}$ is the trace of the considering operator.

@@

Aterwards, considering only the central element ($l=0$) of the inverse scattering time matrix, we can restructure the derived conductivity expression in Eq.~(\ref{eq:29}) as follows

>>>>

A general theory for the conductivity of a dressed system with the disorder was reported by Wackerl \textit{et al.} \cite{wackerl20,wackerlthesis20}. This theory, the general $x$-directional longitudinal DC-limit conductivity has been characterized as
\begin{equation} \label{eq:22}
  \begin{aligned}
    \sigma^{xx} = &
    \frac{-1}{4\pi\hbar A}
    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2}
    \left(
    -\pdv*{f}{\varepsilon }\right) \\
    &  \quad\times
    \tr
    \left\{
    {j}^x_0
    \left[
    \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
    \right]
    {j}^x_0
    \left[
    \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
    \right]
    \right\} d\varepsilon,
  \end{aligned}
\end{equation}
where $j^x_0$ is the $x$-directional electric current operator matrix elements' $0$-th Fourier component. Here, $\vb{G}^{r}(\varepsilon)$ and $\vb{G}^{a} (\varepsilon)$ are the retarded and advanced white noise disorder averaged Floquet Green function matrices \cite{wackerl20,wackerlthesis20}, respectively. These matrices are defined against the Floquet modes of the considering system. Here we have assumed that only $0$-th Fourier component of the current operator is contributing to the conductivity. In addition, $A$ is the area of the considered two-dimensional system, $f$ is the partial distribution function, and $\Pi$ is a function that can be chosen such that
\begin{equation} \label{eq:23}
    \Pi- \flatfrac{\hbar \omega}{2}
    \leq \varepsilon_N
    <
    \Pi + \flatfrac{\hbar \omega}{2}.
\end{equation}
Here $ \varepsilon_N$ are quasienergies of all relevant Floquet states, and $tr\{\cdot\}$ is the trace of the considering operator.

@@

Afterwards, considering only the central element ($l=0$) of the inverse scattering time matrix, we can restructure the derived conductivity expression in Eq.~(\ref{eq:29}) as follows

### 2021-08-20 paper/v2.0/sections/6_manipulate_conductivity.tex
Correction appB
Final corrections
Passive voice corrections
Spelling check

To identify the longitudinal conductivity characteristics of quantum Hall system under external dressing field, first we derive an expression for normalized longitudinal conductivity as a function of Fermi energy $X_F$ and intensity of the dressing field $I$.
We can identifiy the normalized $x$-directional longitudinal conductivity of dressed quantum Hall system by
\begin{equation}\label{eq:37}
  \widetilde{\sigma}^{xx}(X_F,I) =
  \flatfrac{\sigma^{xx}}{\sigma_{0}},
\end{equation}
with $\sigma^0 = \flatfrac{e^2}{(\pi \hbar A)}$, and this can be expressed as
\begin{equation} \label{eq:38}
  \begin{aligned}
    \widetilde{\sigma}^{xx}(X_F,I) &=
    \sum_{n}
    \frac{(n+1)}{\alpha^2 \Lambda_n \Lambda_{n+1}} \\
    &\quad\times
    \left[
      \frac{1}
      {
        1 + \left(\frac{X_F - n -1}{\alpha \Lambda_n}\right)^2
      }
    \right]
    \left[
      \frac{1}
      {
        1 + \left(\frac{X_F - n}{\alpha \Lambda_{n+1}}\right)^2
      }
    \right],
  \end{aligned}
\end{equation}
where $\alpha = \flatfrac{\Gamma_0}{(2\hbar \omega_0)}$. Here, $\Gamma_0$ is the natural energy broadening of the least Landau level.

@@

\begin{figure}[t]
\includegraphics[scale=0.55]{figures/fig_4}
\caption{ Normalized longitudinal conductivity $\widetilde{\sigma}^{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a  frequency of $\omega =\SI{2e12}{\radian\per\second}$ and $I_0 =\SI{100}{\watt\per\square\centi\metre}$. In this calculation, we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $\SI{0.24}{\milli\eV}$.}
\label{fig:5}
\end{figure}

\begin{figure}[t]
\includegraphics[scale=0.55]{figures/fig_5}
\caption{$3$rd Landau level’s normalized longitudinal conductivity $\widetilde{\sigma}^{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a frequency of $\omega =\SI{2e12}{\radian\per\second}$ and $I_0 =\SI{100}{\watt\per\square\centi\metre}$.
In this calculation, we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $\SI{0.24}{\milli\eV}$.}
\label{fig:6}
\end{figure}

>>>>

To identify the longitudinal conductivity characteristics of quantum Hall system under external dressing field, first we derive an expression for normalized longitudinal conductivity as a function of Fermi energy $X_F$ and intensity of the dressing field $I$.
We can identify the normalized $x$-directional longitudinal conductivity of dressed quantum Hall system by
\begin{equation}\label{eq:37}
  \widetilde{\sigma}^{xx}(X_F,I) =
  \flatfrac{\sigma^{xx}}{\sigma_{0}},
\end{equation}
with $\sigma^0 = \flatfrac{e^2}{(\pi \hbar A)}$, and we can express this as
\begin{equation} \label{eq:38}
  \begin{aligned}
    \widetilde{\sigma}^{xx}(X_F,I) &=
    \sum_{n}
    \frac{(n+1)}{\varsigma^2 \Lambda_n \Lambda_{n+1}} \\
    &\quad\times
    \left[
      \frac{1}
      {
        1 + \left(\frac{X_F - n -1}{\varsigma \Lambda_n}\right)^2
      }
    \right]
    \left[
      \frac{1}
      {
        1 + \left(\frac{X_F - n}{\varsigma \Lambda_{n+1}}\right)^2
      }
    \right],
  \end{aligned}
\end{equation}
where $\varsigma = \flatfrac{\Gamma_0}{(2\hbar \omega_0)}$. Here, $\Gamma_0$ is the natural energy broadening of the least Landau level.

@@

\begin{figure}[t]
\includegraphics[scale=0.54]{figures/fig_4}
\caption{ Normalized longitudinal conductivity $\widetilde{\sigma}^{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a  frequency of $\omega =\SI{2e12}{\radian\per\second}$ and $I_0 =\SI{100}{\watt\per\square\centi\metre}$. In this calculation, we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $\SI{0.24}{\milli\eV}$.}
\label{fig:5}
\end{figure}

\begin{figure}[t]
\includegraphics[scale=0.54]{figures/fig_5}
\caption{$3$rd Landau level’s normalized longitudinal conductivity $\widetilde{\sigma}^{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a frequency of $\omega =\SI{2e12}{\radian\per\second}$ and $I_0 =\SI{100}{\watt\per\square\centi\metre}$.
In this calculation, we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $\SI{0.24}{\milli\eV}$.}
\label{fig:6}
\end{figure}
